%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
% \newcommand{\resumeItem}[2]{
%   \item\small{
%     \textbf{#1}{: #2 \vspace{-2pt}}
%   }
% }
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}
\newcommand{\resumeTechItem}[2]{
  \item[]\small{  % The empty [] will remove the bullet point
    \textbf{#1}{}{#2 \vspace{-2pt}}
  }
}
\newcommand{\aresumeSubheading}[4]{
  \vspace{-1pt}
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Justin Whitfield}} & Email : \href{mailto:justinpwhitfield@gmail.com}{justinpwhitfield@gmail.com}\\
  \href{https://justinwhitfield.info}{justinwhitfield.info} & Mobile : \href{tel:+16015693409}{+1-601-569-3409} \\
  \href{https://quizaiapp.com}{quizaiapp.com}\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
    \aresumeSubheading
      {Mississippi State University}{Starkville, MS}
      {Bachelor of Science in Software Engineering;  GPA: 4.00 / 4.00}{Graduating -- May 2024}
    % \resumeSubheading
    %   {Pearl River Community College}{Poplarville, MS}
    %   {Associates of Science;  GPA: 3.40 / 4.00 }{Aug. 2020 -- May 2022}
%-----------EXPERIENCE-----------------
\section{Experience and Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
    {USDA Machine Learning Research}{}
    {Research Position}{Dec 2023 - May 2024}
    \resumeItemListStart
      \resumeItem{}
        {Built a multivariate linear regression model to predict the moisture content of grains based on their dielectric properties, enhancing the efficiency of the grain buy-sell process.}
      \resumeItem{}
        {Developed a system for rapid and accurate determination of moisture percentage (M\%), significantly outperforming classical methods that could take over 20 hours for measurement.}
        \resumeItemListEnd
    \resumeSubheading
      {The Estée Lauder Companies}{Long Island City, NY}
      {Software Engineering Intern}{May 2023 - Aug 2023}
      \resumeItemListStart
        \resumeItem{}
          {Led an Agile team to ideate and develop a generative AI chatbot chat sales assistant for the Origins brand, which provided product recommendations and interacted with customers seamlessly.}
        \resumeItem{}
          {Presented final MVP to global brand president, where permission was granted for further development, a first for an internship project.}
        \resumeItem{}
          {Utilized a vector database of products and made semantic searches through OpenAI API queries and embeddings.}
        \resumeItemListEnd

    \resumeSubheading
      {Quiz-AI iOS App}{}
      {Personal Project}{Oct 2022 - Current}
      \resumeItemListStart
        \resumeItem{}
          {Developed and launched an iOS app that allows users to photograph a question then uses OCR to extract text from the image to provide an AI generated answer. Find out more at quizaiapp.com.}
        \resumeItem{}
          {Integrated OpenAI's API to provide answers to users' questions.}
        \resumeItem{}
          {Implemented Google Ads to offset the API usage costs.}
      \resumeItemListEnd

    \resumeSubheading
      {Recipe Vision}{}
      {School Project}{Aug 2023 - Nov 2023}
      \resumeItemListStart
        \resumeItem{}
          {Fine-tuned a YOLO v7 model on a proprietary dataset of annotated grocery images to recognize ingredients from user-submitted photos.}
        \resumeItem{}
          {Integrated OpenAI API to generate real-time recipes based on the identified ingredients, paired with the Google Images API to dynamically fetch and display images of the generated recipes.}
        \resumeItem{}
          {Engineered a seamless user interface to capture ingredient photos and display recipes, optimizing for user-friendliness and efficiency.}
        \resumeItemListEnd

    \resumeSubheading
      {Nerf Quadruped Robot}{}
      {School Project}{Aug 2023 - Nov 2023}
      \resumeItemListStart
        \resumeItem{}
          {Engineered a specialized control system to integrate a Nerf gun with a Unitree GO1 quadruped robot, achieving automated aiming and firing.}
        \resumeItem{}
          {Implemented object recognition algorithms to identify and track human targets, optimizing robot positioning for accurate shooting.}
        \resumeItem{}
          {Utilized electromagnetic solenoids for triggering the Nerf gun, controlled through serial port communication.}
        \resumeItemListEnd

    \resumeSubheading
    {NetDeals Ecommerce Website}{}
    {School Project}{Aug 2022 - Dec 2022}
    \resumeItemListStart
      \resumeItem{}
        {Designed and implemented a full-stack ecommerce website.}
      \resumeItem{}
        {Features included seller dashboards, product listing creation/deletion, buyer cart functionalities, product comparisons, reporting tools, and return capabilities.}
        \resumeItem{}
        {Backend infrastructure was powered by Django, while the frontend was styled using Bulma CSS.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeTechItem{Languages and Frameworks: }
      {Python, Sklearn, Pytorch, C, C++, Swift, HTML, CSS, Javascript, Flask, Django, React, Tailwind, SQL}
    \resumeTechItem{Developer Tools: }
      {Git, Docker, VS Code, Visual Studio, WSL, Xcode, Linux}
  \resumeSubHeadingListEnd


%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
